Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-20 Manuscript Analyses/manuscript_analysis.Rmd
participant summary updated

cog_scores %>%
  dplyr::group_by(speaker) %>%
  furniture::table1(age, list_sort_c, flanker_c, card_sort_c, vocab_c, pattern_c, 
                    pic_seq_c, fluid_cog_c, best_win,
                    test = T, 
                    export = "cog_score")

>>>>

cog_scores %>%
  dplyr::group_by(speaker) %>%
  furniture::table1(age, list_sort_c, flanker_c, card_sort_c, vocab_c, pattern_c, 
                    pic_seq_c, fluid_cog_c, best_win,
                    test = T, type = c("simple", "condensed"), 
                    export = "cog_score")
